Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-02-28 paper/EDA.qmd
Write up done for summary stats

@tbl-summary-1 shows the summary statistics of game scores before and after treatment. The mean is similar across all groups, indicating no extreme changes in cognitive performance. However, the standard deviation (SD) is relatively high, suggesting some variation among participants.

@@

```{r}
#| label: tbl-summary-1
#| echo: false
#| warning: false
#| message: false

@@

kable(summary_table, format = "latex", booktabs = TRUE, caption = "Summary Statistics for Quantitative Variables") 
```

@@

# Count and percentage for Drug
drug_counts <- table(clean_data$drug)
drug_percentages <- prop.table(drug_counts) * 100
drug_summary <- data.frame(Drug = names(drug_counts), Count = as.numeric(drug_counts), Percentage = round(as.numeric(drug_percentages), 2))
colnames(drug_summary) <- c("Drug", "Count", "Percentage")

# Print tables
kable(drug_summary, format = "latex", booktabs = TRUE, caption = "Summary of Drug Types")

kable(dosage_summary, format = "latex", booktabs = TRUE, caption = "Summary of Dosage Levels")

kable(location_summary, format = "latex", booktabs = TRUE, caption = "Summary of Locations")

kable(age_summary, format = "latex", booktabs = TRUE, caption = "Summary of Age Groups") 
```

>>>>

@tbl-summary-1 shows the summary statistics of memory game scores before and after the treatment. The mean is similar across all groups, indicating no extreme changes in cognitive performance. However, the standard deviation (SD) is relatively high, suggesting some variation among participants.

@@

```{r}
#| label: tbl-summary-1
#| tbl-cap: "Summary Statistics for Quantitative Variables"
#| echo: false
#| warning: false
#| message: false

@@

kable(summary_table, format = "latex", booktabs = TRUE) 
```

## Summary of counts and percentage for qualitative variables

@tbl-summary-2 shows the distribution of participants across drug types. Aspirin, Paracetamol, and Tramadol each have 60 participants (28.57\%), ensuring balance. However, the Placebo group is smaller (30 participants, 14.29\%).

@tbl-summary-3 shows the dosage levels assigned to participants. There is an equal split between high-dose (90 participants, 50\%) and low-dose (90 participants, 50\%) conditions.

@tbl-summary-4 provides an overview of participant locations. The distribution is relatively even across six different locations, with each site having either 30 (14.29\%) or 60 (28.57\%) participants.

## Confounding Variable

@tbl-summary-5 shows the breakdown of age groups, which is a confounding variable in this study. The three age groups: 18–34, 35–50, and 50+ each have 70 participants (33.33\%).

```{r}
#| label: tbl-summary-2
#| tbl-cap: "Summary of Drug Types"
#| echo: false
#| warning: false
#| message: false

# Count and percentage for Drug
drug_counts <- table(clean_data$drug)
drug_percentages <- prop.table(drug_counts) * 100
drug_summary <- data.frame(Drug = names(drug_counts), Count = as.numeric(drug_counts), Percentage = round(as.numeric(drug_percentages), 2))
colnames(drug_summary) <- c("Drug", "Count", "Percentage")
kable(drug_summary, format = "latex", booktabs = TRUE)

```{r}
#| label: tbl-summary-3
#| tbl-cap: "Summary of Dosage Levels"
#| echo: false
#| warning: false
#| message: false

kable(dosage_summary, format = "latex", booktabs = TRUE)

```{r}
#| label: tbl-summary-4
#| tbl-cap: "Summary of Locations"
#| echo: false
#| warning: false
#| message: false

kable(location_summary, format = "latex", booktabs = TRUE)

```{r}
#| label: tbl-summary-5
#| tbl-cap: "Summary of Age Groups"
#| echo: false
#| warning: false
#| message: false

kable(age_summary, format = "latex", booktabs = TRUE) 
```

@@
